---
title: "STA426-HW1-PartB"
format: html
editor: visual
---

## Toy example with Quarto

In order to get familiarized with Quarto, we create a Quarto file where some data is sampled and subsequently plotted.

### Data sampling

The task is to sample 100 values from a negative binomial distribution which is parametrized with a given mean and variance.

The function *rnbinom()* takes mean *mu* and *size* as input. To convert the given variance into *size* a quick calculation is needed.

$$
var = \mu + \mu^2 /size\\
$$
$$
\\
var = \mu + \mu^2*dispersion \\
$$
$$
\\
\rightarrow size = 1/dispersion
$$

Now we can sample the data and store it.

```{r}
n <- 100
mean <- 10
size <- 1/2

sim_data <- rnbinom(n = n, mu = mean, size = size)
```

### Data plotting

For plotting the sampled data either directly or log-transformed in a histogram, we can use the R function *hist().*

```{r}

hist(sim_data, main = "Histogram with linear scale")


```

```{r}
hist(log(sim_data+1), main = "Histogram with logarithmic scale")
```

### Reporting mean and variance of sample

```{r}
sample_mean <- mean(sim_data)
sample_var <- var(sim_data)


```

Sample mean = `r sample_mean` and sample variance = `r sample_var`.
